---
title: "p8105_hw6_nja2140"
author:  Naina Ahuja
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)
library(purrr)
set.seed(10)
```

Problem 1: Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
baby_data=
  read_csv("./Data/birthweight.csv") %>% 
  janitor::clean_names() %>%
  mutate(babysex = factor(babysex, levels =  c("1", "2"), labels = c("male", "female")),
         frace = factor(frace, levels =  c("1", "2", "3", "4", "8", "9"), labels = c("white", "black", "asian", "puerto rican", "other", "unknown")),
         malform = factor(malform, levels =  c("0", "1"), labels = c("absent", "present")),
         mrace = factor(mrace, levels =  c("1", "2", "3", "4", "8"), labels = c("white", "black", "asian", "puerto rican", "other"))
          )
baby_data
```
Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

To figure out the regression model for birthweight, I will run a regression on each individual variable and see which is statistically significantly associated with birthweight. Only the variables that are statistically significant will be included in the regression model. 

```{r}
mp1 = lm(bwt ~ babysex, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp2 = lm(bwt ~ bhead, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp3 = lm(bwt ~ blength, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp4 = lm(bwt ~ delwt, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp5 = lm(bwt ~ fincome, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp6 = lm(bwt ~ frace, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp7 = lm(bwt ~ gaweeks, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp8 = lm(bwt ~ malform, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp9 = lm(bwt ~ menarche, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp10 = lm(bwt ~ mheight, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp11 = lm(bwt ~ momage, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp12 = lm(bwt ~ mrace, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp13 = lm(bwt ~ parity, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp14 = lm(bwt ~ pnumlbw, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp15 = lm(bwt ~ pnumsga, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp16 = lm(bwt ~ ppbmi, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp17 = lm(bwt ~ ppwt, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp18 = lm(bwt ~ smoken, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
mp19 = lm(bwt ~ wtgain, data = baby_data) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) 
```

```{r}
fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + momage + mrace + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = baby_data) 
fit
```

```{r}
plot_1 = 
  baby_data %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point () +
  labs(
    title = "Predicted Birthweight vs Residuals",
    x = "Predicted Birthweight  (grams)",
    y = "Residuals"
  )
plot_1
```
Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
fit_1 = lm(bwt ~ blength + gaweeks, data = baby_data) %>% 
  broom::tidy() %>% 
  knitr::kable()
```

```{r}
fit_2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + babysex*blength + bhead*blength*babysex, data = baby_data) %>% 
  broom::tidy() %>% 
  knitr::kable()
```
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
cv_df = 
  crossv_mc(baby_data, 100) 

cv_df = 
  cv_df %>% 
  mutate(fit = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + momage + mrace + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = .x)),
         fit_1 = map(train, ~lm(bwt ~blength + gaweeks, data = .x)),
         fit_2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + babysex*blength + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_fit = map2_dbl(fit, test, ~rmse(model = .x, data = .y)),
         rmse_fit_1 = map2_dbl(fit_1, test, ~rmse(model = .x, data = .y)),
         rmse_fit_2 = map2_dbl(fit_2, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything (),
    names_to = "model", 
    values_to = "rmse", 
    names_prefix = "rmse_") %>% 
  mutate(model - fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin () +
  labs(
    title = "Root Mean Square Error for each proposed model",
    x = "Model",
    y = "Root Mean Square Error (RMSE)"
  )
```
From this plot, we can see model 1 is the best because the root mean square error is the smallest.

Problem 2: Download the data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data. Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. 

Running the simple linear regression:
```{r}
lm(tmax ~ tmin, data = weather_df) %>% 
  broom::tidy()
```
Bootstrap samples:
```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

Drawing 5000 boostrap samples
```{r}
boot_straps =
  tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
```
Estimates:

```{r}
boot_strap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(cols = c(results)) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  janitor::clean_names() %>% 
  mutate(log = log(intercept*tmin)) %>% 
  select(strap_number, log)
boot_strap_results
```
```{r}
boot_strap_r2 =
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data=.x)),
    results = map(models, broom::glance)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(cols = c(results)) %>% 
  select(strap_number, r.squared)
boot_strap_r2
```
Plot the distribution of your estimates, and describe these in words.
```{r}
plot_2 = 
  boot_strap_results %>% 
  ggplot(aes(x  = log)) +
  geom_density()
plot_2 +
  labs(
    title = "Distribution of estimates for  log(B0*B1)",
    x = "Log(B0*B1)",
    y = "Estimates"
  )
```
This  distribution of  estimates looks approximately normal.
```{r}
plot_3 = 
  boot_strap_r2 %>% 
  ggplot(aes(x  = r.squared)) +
  geom_density()
plot_3 +
  labs(
    title = "Distribution of estimates for R Squared",
    x = "R Squareed",
    y = "Estimates"
  )
plot_3
```
The distribution of the r squared estimates looks slightly left skewed. 

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1).
```{r}
log_ci=
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(tmax ~ tmin, data = .x)),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(.id) %>% 
  summarize(log_coef = sum(log(estimate))) %>% 
  summarize(low_int = quantile(log_coef, 0.025), up_int = quantile(log_coef, .975))
log_ci
```

```{r}
r2_ci =
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(tmax ~ tmin, data = .x)),
         results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  summarize(low_int = quantile(r.squared, 0.025), up_int = quantile(r.squared, .975))
r2_ci
```



